---
title: "SHARP setup for Pacific Northwest"
output:
  html_document:
    df_print: paged
---

This is a preliminary visualization of the SHARP setup for PNW.

MetSim -> SUMMA -> MizuRoute

## Temporal plots

```{r loadinglibraries}
library(rgdal)
library(ggplot2)
library(dplyr)
library(ncdf4)
library(RColorBrewer)
library(data.table)
```

```{r}
pnw <-readOGR(dsn ="/glade/p/work/manab/SHARP/shapefiles/naokifiles/", layer = 'Region_17_merged_hru')

```

### Inputs

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

